### 2018-08-02 article.tex
fixed typo
Mathematical Preliminaries: Quantale / Q-enriched category / Monoidal Q-enriched category

@@

\section{\mathbb{Q}-valued rewriting systems}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        QUANTALE DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quantale}

Let's define the following quantale $\mathbb{Q}$ over a \emph{group}, which is a monoidal category

\begin{itemize}
\item objects are elements of a lattice $L$
\item for all objects $(x, y)$ there is a morphism between $x$ and $y$ iff $x \succeq y$ in $L$.
\item a unit objet $e \in L$
\item a monoidal operator $\oplus: Q \times Q \to Q$
\end{itemize}

\noindent such that for all $x, y \in L$ and $\{x_i\}_i, \{y_i\}_i \subseteq L$
\begin{align}
x \oplus \bigvee y_i &= \bigvee x \oplus y_i \cr
\left(\bigvee x_i\right) \oplus y &= \bigvee x_i \oplus y
\end{align}

We require that for all objects $x$ of $\mathbb{Q}$, it exist an object $x^{-1}$ such that
\begin{align}
x \oplus x^{-1} &= e \cr
x^{-1} \oplus x &= e
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathbb{Q}$-enriched category}

A $\mathbb{Q}$-enriched category \catE is

\begin{itemize}
\item A set of objects
\item For all objects $(a, b)$, $\catE(a, b) \in \mathbb{Q}$
\end{itemize}

such that for all object $a$
$$
e \succeq \catE(a, a)
$$
for all objects (a, b, c)
$$
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
$$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Monoidal $\mathbb{Q}$-enriched category}

$(E, \otimes)$ is strictly monoidal if
$$
\catE(a, b) \oplus \catE(a', b') \succeq \catE(a \otimes a', b \otimes b')
$$
and symmetric if
$$
e \succeq \catE(a \otimes b, b \otimes a)
$$

@@

\section{$\mathbb{Q}$-valued rewriting systems}
